A data-intensive assessment of the species-abundance distribution.

### 2015-03-22 defense_pres.tex
Tweaks formatting.
Typo.
Adds shiny, shiny illustrations because I have no fieldwork pictures.

\section{Introduction}
\subsection{What is macroecology?}
\begin{frame}[t]
\frametitle{Macroecology}
\normalsize One approach to studying ecological patterns and processes.\\
\begin{itemize}
\item Data intensive.
\item Large scales
\begin{itemize}
\item Spatial
\item Temporal
\item Taxonomic
\end{itemize}
\item Search for generality.
\end{itemize}
\end{frame}

@@

\subsubsection{Data Summary}
\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.5]{./sad-data/chapter2/bioregions.png}
\end{frame}

@@

@@

\section{Acknowledgements}
\begin{frame}[t]{}
\frametitle{Acknowledgements}
~\\ %Adds vertical space for better aesthetics
\small{Funding sources:}
\begin{tiny}
\begin{itemize}
\item USU Department of Biology
\item Intellectual Ventures private funding to Morgan Ernest
\item National Science Foundation CAREER Grant to Ethan White
\item Gordon \& Betty Moore Foundation's Data-Driven Discovery Initiative Grant to Ethan White.
\item USU Graduate School Dissertation Fellowship
\end{itemize}
\end{tiny}
\end{frame}

@@

\subsection{Accessibility}
\begin{frame}[t]{}
\frametitle{Accessibility}
\begin{flushright}
This dissertation brought to you by:
\end{flushright}
\begin{Large}
Disability accommodations\\
\end{Large}
~\\
\begin{itemize}
\item Remote access \& participation.\\
\item Computational tools \& tricks.
\begin{itemize}
\item Version control (GitHub).
\item Publicly available data.
\item Programming skills (data manipulation \& analysis).
\end{itemize}
\end{itemize}
\end{frame}

>>>>

\section{Introduction}
\subsection{What is macroecology?}
\begin{frame}[t]
\frametitle{Macroecology}
\normalsize One approach to studying ecological patterns and processes.\\
\begin{itemize}
\item Data intensive.
\item Large scales.
\begin{itemize}
\item Spatial
\item Temporal
\item Taxonomic
\end{itemize}
\item Search for generality.
\end{itemize}
\end{frame}

@@

\subsubsection{Data Summary}
\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.4]{../Miscellaneous/Pictures/Phd/CompiledData.png}
\end{frame}

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.5]{./sad-data/chapter2/bioregions.png}
\end{frame}

@@

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.4]{../Miscellaneous/Pictures/Phd/MapCreatures.png}
\end{frame}

@@

\section{Acknowledgements}
\begin{frame}[t]{}
\frametitle{Acknowledgements}
~\\ %Adds vertical space for better aesthetics
\small{Funding sources:}
\begin{small}
\begin{itemize}
\item USU Department of Biology
\item Intellectual Ventures, private funding to Morgan Ernest
\item National Science Foundation CAREER Grant to Ethan White
\item Gordon \& Betty Moore Foundation's Data-Driven Discovery Initiative Grant to Ethan White.
\item USU Graduate School Dissertation Fellowship
\end{itemize}
\end{small}
\end{frame}

@@

\subsection{Accessibility}
\begin{frame}[t]{}
\frametitle{Accessibility}
\begin{center}
This dissertation brought to you by:
\end{center}
\begin{Large}
Disability accommodations\\
\end{Large}
~\\
\begin{itemize}
\item Remote access \& participation.\\
\item Computational tools \& tricks.
\begin{itemize}
\item Version control (GitHub).
\item Publicly available data.
\item Programming skills (data manipulation \& analysis).
\end{itemize}
\end{itemize}
\end{frame}
